based on new tutorial https://dataquality.ship-med.uni-greifswald.de/VIN_DQ-report-SHIP-example.html
using  older DQ-report-example-SHIP.Rmd for loading

### Summary table
```{r message=FALSE, echo=FALSE, warning=FALSE}
MyValueLimits_ship$SummaryTable
```


### Summary plot
```{r }
# select variables with deviations
whichdeviate_ship <- as.character(MyValueLimits_ship$SummaryTable$Variables)[MyValueLimits_ship$SummaryTable$GRADING == 1]
head(MyValueLimits_ship$SummaryPlotList[whichdeviate_ship], 2)
```

comparing plots from dataquiR

```{r }
# plots
dataquiR_plot <- MyValueLimits_ship$SummaryPlotList$AGE_0
dataquiR_plot
dataquiR_data <- MyValueLimits_ship$SummaryPlotList$AGE_0$data$AGE_0
dataquiR_hist <- hist(dataquiR_data)

# data for plots
print("dataquiR plot data")
dataquiR_data
print("dataquiR hist data")
dataquiR_hist
```

generate random sample 

```{r }

dataquiR_size <- length(dataquiR_data)
dataquiR_max <- max(dataquiR_data)
random_data <- sample(x = 0:dataquiR_max+3, size = dataquiR_size, replace = TRUE)

plot(dataquiR_hist)
random_hist <- hist(random_data)

# data for plots
print("dataquiR hist data")
dataquiR_hist
print("random sample hist data")
random_hist

```

KS test
one sample test
"What is the probability that this collection of samples could have been drawn from that probability distribution?" <- only this for validation!
two sample test
"What is the probability that these two sets of samples were drawn from the same (but unknown) probability distribution?"

The idea behind the KS test is simple: if two samples belong to each other, their empirical cumulative distribution functions (ECDFs) must be quite similar. This suggests that we can evaluate their similarity by measuring the differences between the ECDFs.

To achieve this, the KS test finds the maximum distance between the ECDFs. More importantly, the test requires evaluating whether the distance is large enough to claim that the two samples do not belong to each other.
https://towardsdatascience.com/how-to-compare-two-distributions-in-practice-8c676904a285

KS test for age

```{r }

# perform a two-sample Kolmogorov-Smirnov test 
# on data
print("KS test on data")
ks.test(random_data,dataquiR_data)

# ecdf
dataquiR_ecdf<- ecdf(x = dataquiR_data)
random_ecdf <- ecdf(x = random_data)

# ks with ecdf
print("KS test with ecdf")
ks.test(random_data,dataquiR_ecdf)

# plot ecdf
plot(dataquiR_ecdf, main = "ECDF of dataquiR_data and random_data")
lines(random_ecdf, col = 2)

# ks verification
print("KS test with second sample")
ks.test(sample(x = 0:dataquiR_max+3, size = dataquiR_size, replace = TRUE),random_ecdf)


```

required data for validation
ecdf
D, p-value limits


```{r }
# save ecdf as .rds
saveRDS(dataquiR_ecdf, file = "dataquiR_ship_ecdf_age.rds")

ship_contradiction_checks <- read.csv(file = "ship_contradiction_checks.csv", sep ="#")
```

TODO:
- what about one sided test? WITH ecdf always onesided
- D, p-value limits; D high, p low means not from same dist

testing

```{r }
# read ship meta from csv
ship_contradiction_checks <- read.csv(file = "ship_contradiction_checks.csv", sep ="#")
ship_missing_codes <- read.csv(file = "Missing-Codes-SHIP.csv", sep =";")

# read xlx from clipboard
westorm_datacatalog <- read.table(file = "clipboard", sep = "\t", header=TRUE)

```

